Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-15 csf-2017/paper.tex
store-local => write-local.

However, if we are returning from a function that has itself invoked adversary
code, then clearing the used part of the stack is not enough. The \emph{unused}
part of the stack may also contain data and capabilities, left there by the
adversary, including local capabilities since the stack is store-local. The
adversary could take advantage of this by using the unused part of the stack to
store either stack pointers or return pointers from such previous invocations
and then use them when they're no longer supposed to. To prevent this, we need
to clear (i.e.\ overwrite with zeros) the entire part of the stack that the
adversary has had access to, not just the parts that we have used ourselves.
This requirement may seem strong, but it is essentially there for the same
reason that we clear the register file: the adversary should not be able to keep
hold of local capabilities when control is passed to trusted code and back to
the adversary. Since we may be talking about a large part of memory, this is the
most problematic aspect of our calling convention for performance, but see
Section~\ref{sec:discussion} for how this might be mitigated.

>>>>

However, if we are returning from a function that has itself invoked adversary
code, then clearing the used part of the stack is not enough. The \emph{unused}
part of the stack may also contain data and capabilities, left there by the
adversary, including local capabilities since the stack is write-local. The
adversary could take advantage of this by using the unused part of the stack to
store either stack pointers or return pointers from such previous invocations
and then use them when they're no longer supposed to. To prevent this, we need
to clear (i.e.\ overwrite with zeros) the entire part of the stack that the
adversary has had access to, not just the parts that we have used ourselves.
This requirement may seem strong, but it is essentially there for the same
reason that we clear the register file: the adversary should not be able to keep
hold of local capabilities when control is passed to trusted code and back to
the adversary. Since we may be talking about a large part of memory, this is the
most problematic aspect of our calling convention for performance, but see
Section~\ref{sec:discussion} for how this might be mitigated.
